Finding Bugs in JavaScript Engines with Differential Testing

### 2018-05-13 docs/google-research-awards-latam/main.tex
polishing + pass on abstract

\vspace{-2ex}
\begin{abstract}
  \Fix{...}
\end{abstract}

@@

Differential testing\cite{McKeeman98differentialtesting} has been
applied in a variety of
contexts\cite{Brumley-etal-ss07,Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17},
but it has not been thoroughly explored to find functional bugs in JS
engines. The closest work was done by Patra and
Pradel~\cite{patra2016learning}, where they evaluated their proposed
language-agnostic fuzzer to find cross-browser HTML+JS
discrepancies. This project aims to provide an adaptable
infrastructure for differential testing of runtime engines, such as
the JS engine or WebAssembly's. The sensible parts of the
infrastructure are the checks of input validity (as to reduce
waste/cost) and output correctness (as to reduce false positives).

@@

\begin{wrapfigure}[10]{r}[0pt]{0.45\textwidth}
  \vspace{-5ex}
  \centering
  \includegraphics[trim=20 350 200 0,clip,width=0.45\textwidth]{google-awards-workflow}
  \caption{\label{fig:workflow}Fuzzing Infrastructure.}
  \vspace{-5ex}  
\end{wrapfigure}
Fuzzing is a popular technique to generate new test inputs from
existing inputs~\cite{fuzz-testing-history} with the typical goal of
finding crashes. Several fuzzing methods have been proposed in the
past, varying with respect to how new inputs are generated (\eg{},
coverage-based~\cite{afl,honggfuzz},
grammar-based~\cite{grammarinator,jsfunfuzz}, and
random-based~\cite{radamsa}) and whether or not coverage information
is taken into account in the fuzzing
process. Figure~\ref{fig:workflow} shows a generic pipeline of a
fuzzer, instantiated to our problem. Arrows indicate data flow; lines
with no arrow denote encapsulation. In our case, JS files are
provided as seeded inputs to bootstrap the process. These files can
originate from the test suites of the engine codebases or from the bug
reports in their issue trackers. The fuzzing infrastructure selects
randomly one of the inputs to fuzz with a given tool, say the
black-box fuzzer Radamsa~\cite{radamsa}. Each fuzzing iteration
produces a new file. For grammar-agnostic fuzzers, like Radamsa, the
infrastructure needs to detect and discard syntactically invalid
inputs. Semantically invalid inputs are detected dynamically or with
linters. Once the input is found to be valid, the infrastructure
invokes the oracle to check correctness. In case all engines
consider the test output consistent (\ie{}, all pass or all fail), the
infrastructure discards the corresponding input. Otherwise, it considers that
input as potentially fault-revealing and interesting. Currently, we
classify alarms in two groups: HI and LO. The HI group includes
those warnings that manifest execution errors spawned directly by the
test (or its close neighborhood) whereas the LO group includes the
rest of the warnings. We found empirically that \Fix{XX\%} of the
warnings analyzed in the HI group were confirmed (see
Section~\ref{sec:results})

@@

Although there are many features yet to implement in our
infrastructure, the basic workflow described in
Section~\ref{sec:design} is functional. This section shows preliminary
results providing some evidence that finding bugs in runtime engines is
promising. Table~\ref{tab:bugs} shows the list of bugs we reported on
issue trackers of different engines in the period of a month. For
example, bug \# 6 was manifested by the JS code \CodeIn{var a =
  \{valueOf:~function()\{return ``\textbackslash{}x00''\}\} assert(+a
  === 0)\}}\footnote{This is a Lithium-minimized~\cite{lithium}
  version of the fuzzed code.}. In the original version of this code the \CodeIn{valueOf} function returned
the empty string, whose integer representation according to the spec
should be zero\Fix{check part of spec to link}. The modified
code returns a string representation of an invalid hexadecimal
value. The engines should not be able to evaluate that string at
the assertion expression\Fix{explain why}. MS Chakra, however, is able to parse it
returning a null object. In addition, the test passes as it converts
null to zero.

\newcommand{\checkm}{Y}
\newcommand{\crossmark}{N}
\begin{wraptable}[16]{tr}[0pt]{0.5\textwidth}
  \vspace{-4ex}
  \scriptsize
  \centering
  \caption{List of bug reports issued by our team from April 12 to May
    10, 2018.}
  \label{tab:bugs}
  \begin{tabular}{cccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}   \\
    \midrule    
    1  & 4/12 & \checkm & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}      \\ 
    2  & 4/12 & \checkm & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}      \\
    3  & 4/14 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}        \\
    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}        \\
    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}       \\
    6  & 4/25 & \checkm & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}      \\
    7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}
    \\
    \midrule
    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} \\
                        & \checkm &                       &
    JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}    \\
    \midrule    
    9  & 4/29 & \checkm & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}    \\
    \midrule    
    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{\checkm} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} \\    
                        &                        &        &
    JavascriptCore & New &
    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}
    \\
    \midrule    
    11 & 5/02 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}\\
    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}\\
    13 & 5/10 & \crossmark & Chakra & New & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} \\
   \bottomrule     
  \end{tabular}
\end{wraptable}
So far, six of the bugs we reported
were confirmed, two of which were fixed. One bug report we
submitted was rejected on the basis that the offending JS file
manifested an expected incompatibility across engine
implementations.
Note from the table that, with the exception of one case, all bug
reports still waiting for confirmation are associated with the
JavaScriptCore engine (JSC). A closer look at the JSC issue tracker
showed that the triage process is very slow for that engine. As of
now, we did not find any bug on SpiderMonkey and V8. Finally, it is
worth noting that seven of the 13 JS files that manifested
discrepancies were produced with fuzzing (column ``Fuzz''). This
emphasizes the importance of continuously collecting test suites from
multiple sources; today, we use test suites from six different open
source engines, including a total of \Fix{38.9K} test files.

>>>>

\vspace{-2ex}
\begin{abstract}
JavaScript (JS) is a fundamental programming language for the
web. Finding bugs in JavaScript engines is an important
problem. Differential testing of JS engines is a promising approach to
that end. This proposal describes our testing infrastructure, current
results, and some upcoming features to improve the bug-finding
process.
\end{abstract}

@@

Differential testing\cite{McKeeman98differentialtesting} has been
applied in a variety of
contexts\cite{Brumley-etal-ss07,Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17}
to mitigate with the lack of oracles problem,
but it has not been thoroughly explored to find functional bugs in JS
engines. The closest work was done by Patra and
Pradel~\cite{patra2016learning}, where they evaluated their proposed
language-agnostic fuzzer to find cross-browser HTML+JS
discrepancies. This project aims to provide an adaptable
infrastructure for differential testing of runtime engines, such as
the JS engine or WebAssembly's. The sensible parts of the
infrastructure are the checks of input validity (as to reduce
waste/cost) and output correctness (as to reduce false positives).

@@

\begin{wrapfigure}[10]{r}[0pt]{0.45\textwidth}
  \vspace{-5ex}
  \centering
  \includegraphics[trim=20 350 200 0,clip,width=0.45\textwidth]{google-awards-workflow}
  \caption{\label{fig:workflow}Fuzzing Infrastructure.}
  \vspace{-5ex}  
\end{wrapfigure}
Fuzzing is a popular technique to generate new test inputs from
existing inputs~\cite{fuzz-testing-history} with the typical goal of
finding crashes. Several fuzzing methods have been proposed in the
past, varying with respect to how new inputs are generated (\eg{},
coverage-based~\cite{afl,honggfuzz},
grammar-based~\cite{grammarinator,jsfunfuzz}, and
random-based~\cite{radamsa}) and whether or not coverage information
is taken into account in the fuzzing
process. Figure~\ref{fig:workflow} shows a generic pipeline of a
fuzzer infrastructure, instantiated to our problem. Arrows indicate data flow; lines
with no arrow denote encapsulation. In our case, JS files are
provided as seeded inputs to bootstrap the process. These files can
originate from the test suites of the engine codebases or from the bug
reports in their issue trackers. The fuzzing infrastructure selects
randomly one of the inputs to fuzz with a given tool, say the
black-box fuzzer Radamsa~\cite{radamsa}. Each fuzzing iteration
produces a new file. For grammar-agnostic fuzzers, like Radamsa, the
infrastructure can discard syntactically invalid
inputs using an external parser for the input language; semantically
invalid inputs can be prevented with with linters. Once the input is
found to be likely valid, the infrastructure
invokes the oracle to check correctness. In case all engines
consider the test output consistent (\ie{}, all pass or all fail), the
infrastructure discards the corresponding input. Otherwise, it considers that
input as potentially fault-revealing and interesting. Currently, we
classify alarms in two groups: HI and LO. The HI group includes
those warnings that manifest execution errors spawned directly by the
test (or its close neighborhood) whereas the LO group includes the
rest of the warnings. We found empirically that \Fix{XX\%} of the
warnings analyzed in the HI group were confirmed.

@@

%% Although there are many features yet to implement in our
%% infrastructure,

The basic workflow described in Section~\ref{sec:design} is functional. This section shows preliminary
results obtained with our infrastructure providing some evidence that finding bugs in runtime engines is
promising. Table~\ref{tab:bugs} shows the list of bugs we reported on
issue trackers of different engines in the period of a month. For
example, bug \# 6 was manifested by the JS code \CodeIn{var a =
  \{valueOf:~function()\{return ``\textbackslash{}x00''\}\} assert(+a
  === 0)\}}\footnote{This is a Lithium-minimized~\cite{lithium}
  version of the fuzzed code.}. In the original version of this code, the \CodeIn{valueOf} function returned
the empty string, whose integer representation, according to the spec,
should be zero\Fix{igor, please look for the part of spec and add link}. The modified
code returns a string representation of an invalid hexadecimal
value\Fix{igor, how do we know this is invalid?}. As such, the engines
are not expected to evaluate that string at the assertion expression;
hence test execution is expected to fail. Chakra,
however, is able to parse the string as a number. It returns a null
object, which is then converted to zero, making the test to pass.
\newcommand{\checkm}{Y}
\newcommand{\crossmark}{N}
\begin{wraptable}[20]{tr}[0pt]{0.5\textwidth}
  \vspace{-2ex}
  \scriptsize
  \centering
  \caption{List of bug reports issued by our team from April 12 to May
    10, 2018.}
  \label{tab:bugs}
  \begin{tabular}{cccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}   \\
    \midrule    
    1  & 4/12 & \checkm & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}      \\ 
    2  & 4/12 & \checkm & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}      \\
    3  & 4/14 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}        \\
    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}        \\
    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}       \\
    6  & 4/25 & \checkm & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}      \\
    7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}
    \\
    \midrule
    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} \\
                        & \checkm &                       &
    JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}    \\
    \midrule    
    9  & 4/29 & \checkm & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}    \\
    \midrule    
    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{\checkm} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} \\    
                        &                        &        &
    JavascriptCore & New &
    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}
    \\
    \midrule    
    11 & 5/02 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}\\
    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}\\
    13 & 5/10 & \crossmark & Chakra & New & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} \\
   \bottomrule     
  \end{tabular}
\end{wraptable}

So far, six of the bugs we reported
were confirmed, two of which were fixed. One bug report we
submitted was rejected on the basis that the offending JS file
manifested an expected incompatibility across engine
implementations.
Note from the table that, with the exception of one case, all bug
reports still waiting for confirmation are associated with the
JavaScriptCore engine (JSC). A closer look at the JSC issue tracker
showed that the triage process is very slow for that engine. As of
now, we did not find any bug on SpiderMonkey and V8. Finally, it is
worth noting that six of the 13 JS files that manifested
discrepancies were \emph{not} produced with fuzzing (column
``Fuzz''). These are test files from suites of different engines. This
observation emphasizes the importance of continuously collecting test suites from
multiple sources; today, we use test suites from six different open
source engines, including a total of \Fix{38.9K} test files.
